Analysis paper

### 2021-08-20 analysis/analysis.Rmd
update plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)

@@

@@

  trend <- 
    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
                                               "s", " in ", location_name)]
  setnames(trend, old = c("classification"), new = c("Classification"))
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.4,
                   alpha = 1,
                   position = position_dodge(width = 4.6)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

@@

@@

  p_cov50 <- scores[range %in% c(50)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.9, linetype = "dashed") +
    labs(y = "Coverage - 90% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_combined <- (p_mean + p_aem) / 
    (p_sharpness + p_bias) / 
    (p_cov50 + p_cov90) /
    (p_wis_sd) +  
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom')

  ggsave(here(output_dir, paste0(plotname, ".png")), 
         height = 9.1, width = 10)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)
library(tidyr)
library(forcats)

@@

  # data = unfiltered_data[model %in% regular_models]
  # df <- data[quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
  #   dcast(... ~ quantile, value.var = "prediction")
  # df <- merge(
  #   df[, c("classification", "speed") := NULL], 
  #   copy(epitrend)[, c("forecast_date", "true_value") := NULL], 
  #   by = c("target_end_date", "location_name", "target_type")
  # )
  # df <- df[grepl(2, target)]

@@

  trend <- 
    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
                                               "s", " in ", location_name)]
  setnames(trend, old = c("classification"), new = c("Classification"))
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.1,
                   alpha = 1,
                   position = position_dodge(width = 3.6)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    theme(panel.grid.major.x = element_blank()) +
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)), 
                 minor_breaks = forecast_dates$unfiltered + 5)
  return(p)
}

@@

  data <- filtered_data[model %in% regular_models]

  scores <- eval_forecasts(data, 
                           summarise_by = c("model", "target_type", "horizon"), 
                           quantiles = 0.5, 
                           sd = TRUE)

  component_plot <- function(scores, type) {

    if (type == "case") {
      vals <- colcases
    } else {
      vals <- coldeaths
    }

    scores %>%
      select(Model, target_type, horizon, sharpness, interval_score,
             underprediction, overprediction) %>%
      filter(target_type == type) %>%
      pivot_longer(names_to = "WIS components",
                   cols = c(sharpness, overprediction, underprediction)) %>%
      mutate(`WIS components` = fct_relevel(`WIS components`, 
                                            c("sharpness", "underprediction", 
                                              "overprediction"))) %>%
      group_by(target_type, horizon) %>%
      arrange(interval_score) %>%
      ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
                 group = Model, alpha = `WIS components`)) + 
      scale_alpha_manual(values = c(1, 0.1, 0.6)) +
      scale_fill_manual(values = vals) + 
      geom_bar(stat = "identity", position = "stack",
               color = "black",
               size = 0.1,
               width = 0.8) +
      facet_wrap(~ horizon, ncol = 4,
                 strip.position="bottom") + 
      theme_minimal() + 
      theme(axis.text.x = element_blank(), 
            plot.title = element_text(hjust = 0.5, 
                                      size = 8), 
            legend.position = c(0.12, 0.83)) + 
      labs(x = NULL, title = type, y = "WIS") + 
      guides(fill = "none")
  }

  component_case <- component_plot(scores, "case")
  component_death <- component_plot(scores, "death")
  components <- component_case + component_death

@@

  p_cov50 <- scores[range %in% c(50)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI") + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.9, linetype = "dashed") +
    labs(y = "Coverage - 90% PI") + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_combined <- (p_mean) / 
    (p_cov50) /
    (p_cov90) / 
    (component_case + component_death) +  
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom', 
          legend.box="vertical", legend.margin=margin())

  ggsave(here(output_dir, paste0(plotname, ".png")), 
         height = 9.1, width = 8)

  p_combined2 <- (p_aem + p_wis_sd) /
    (p_sharpness + p_bias) + 
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom', 
          legend.box="vertical", legend.margin=margin())

    ggsave(here(output_dir, paste0(plotname, "-2.png")), 
         height = 5.1, width = 10)

    p_combined3 <- (p_mean + p_aem) /
        (p_cov50 + p_cov90) /
        (p_sharpness + p_bias) /
        (p_wis_sd + plot_spacer()) + 
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A')  &
    theme(legend.position = 'bottom', 
          legend.box="vertical", legend.margin=margin())

    ggsave(here(output_dir, paste0(plotname, "-3.png")), 
         height = 9.1, width = 10)

    p_combined4 <- 
      components / 
      (p_cov50 + p_cov90) /
      (p_sharpness + p_bias) /
      (p_aem + p_wis_sd) +
    plot_layout(guides = "collect", 
                heights = c(1.3, 1, 1, 1)) &
    plot_annotation(tag_levels = 'A')  &
    theme(legend.position = 'bottom', 
          legend.box="vertical", legend.margin=margin())

    ggsave(here(output_dir, paste0(plotname, "-4.png")), 
           height = 9.1, width = 10)
}
